Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-27 WRITEUP/ms.tex
updated Sec 3

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCs) in a cosmological zoom-in simulation of a
prototypical galaxy (``\flower'') at redshift $z\approx 6$.
%
We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
%mm (gas+stars), 
    taking into account both gas and stars, 
and by using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
%mm
    instability to gravitational 
collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish 
%mm scrutinizing 
data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular 
%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
   cloud complexes (MCCs)  \MM{changed MC to MCC throughout}
that are typically more massive ($M_{\rm cl}\approx 10^9$\,\Msun) and extended ($\approx$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

% ------------------
\section{Numerical simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, 
%mm resolving down to a physical scale of 
     with the finest refined cell sizes 
$l_{\rm cell}\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution
%mm
    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
    local density, which would have to be specified here.}
 of $m_b\simeq$\,10$^4$\,\Msun at the finest level. 
%mm Such a physical scales are comparable to those of
     Cell sizes are comparable to the sizes of
local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%mm 
     \MM{Nota Bene!} although the resolved scale of 5--10 cells is rather larger.

%mm We
    The models 
include a chemical network 
%mm including ${\rm e}^{-}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ 
   following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$
\citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme 
%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
    described by \citet{Pallottini17a}.

% radiative feedback --> NT pressure
Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) 
%mm and OB/AGB stars. 
   as well as OB and asymptotic giant branch stars.
Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell. The remaining energy is injected into the ISM in kinetic and thermal energy forms. Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).  
%mm
   \MM{confirm:} Photoionization and stellar wind feedback is neglected.

The simulation zooms in on a galaxy named
%mm 
   after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
%mm (LBG), [unused acronym]
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne. \MM{What is its gas fraction?  I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\approx$15\,kpc).} of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\approx 700$ Myr.

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\approx 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10$-$13 MCCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$. The mass of the MCCs identified ranges between $M_{\rm cl}\approx$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCCs?}

@@

MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \approx 100 {\rm km s}^{-1}$) and sizes ($R\approx 100$ pc). These values are consistent with those found in starburst galaxies as SMM J2135-0102, located at $z=...$ \AF{Give refs. here and in caption; in addition it would good to give the properties of this galaxy}.
Sizes are somewhat dependent on the choice of $n_{\rm cut}$. As such density threshold is increased, some of the MCCs within the main disk break into multiple sub-MCCs. In this case, we effectively identify a population of denser molecular structures (see \Fig{MCC}). Instead, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.

@@

%
%\begin{comment}
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
%\caption{
%Larson's (linewidth-size) relation of \flower in
%accretion phase (top) and
%starburst phase (bottom) compared to
%those observed in nearby and the \z$\sim$2 star-forming galaxy.
%% Red lines show the relation obtained from \citet{}.
%Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
%\label{fig:larsons_single}}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
%\caption{
%Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel)
%and the starburst phase (bottom panel) compared to the
%Milky Way (other symbols).
%Literature data are compiled from \citealt{Kauffmann17b} and references therein.
%Star symbols are color-coded by $n_{\rm cut}$.
%Star symbols lying close to $\alpha_{\rm vir}\approx2$ correspond to MCCs in the satellite galaxies.
%\label{fig:alpha16}}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
%\caption{
%$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCCs identified in our simulation (star symbols)
%in the accretion phase (top panel) and the starburst phase (bottom panel)
%compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
%The V-shaped dashed lines show the loci along which the given external pressures
%are needed for MCCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
%Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
%Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
%correspond to MCCs in the satellite galaxies.
%\label{fig:alpha27}}
%\end{figure*}
%\end{comment}

@@

The MCCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCCs also have higher stellar-to-gas mass ratios of $\sim$60).
%
In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\approx$10\,\kms).

@@

Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a
velocity dispersion of $\sigma\approx50$\,\kms and a
gas mass surface density of $\Sigma_{\rm gas}\approx450$\,\Msun\,pc$^{-2}$ yields
$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCCs identified (see \Fig{dist}).
%
Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions. That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\approx$\,30\,pc).

@@

% alpha parameters
As shown in \Fig{larsons_single},
the virial parameter of the sub-MCCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
%
For the MCCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\approx$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellites as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).

@@

We find that the MCC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCCs is of the order of $10^{5.5-8.5}$\,\Msun, depending on the chosen H$_{2}$ cut. 
The $\sim$200\,pc-scale MCCs found with a low density threshold
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
The more massive and bigger MCCs in \flower compared to the Milky Way
likely result from the higher gas mass fraction, surface density, and velocity dispersion,
which set the scale for fragmentation.
This physical scale is
consistent with what has been found in higher resolution idealized simulation of isolated galaxies.
Our simulation here confirms these results at EoR and under
the influence of continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).

>>>>

\begin{abstract}
%mm rearranged sentence
We study the properties of molecular cloud complexes (MCs) in a cosmological zoom-in simulation of a
prototypical galaxy (``\flower'') at redshift $z\simeq 6$.
%
We identify MCs using an H$_2$ density-based clump finder, and compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) with those observed in nearby and \z$\lesssim 2$ galaxies.
%
In \flower, MC masses are in the range $10^{5.5-8.5}$\,\Msun, and have sizes $R\lesssim200$\,pc. Their velocity dispersion and gas surface density are systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
%
We identify gravitationally unstable MCs both via an effective, two-component Toomre $Q_{\rm eff}$ parameter 
%mm (gas+stars), 
    taking into account both gas and stars, 
and by using a more observationally accessible $\alpha_{\rm vir}$ analysis. We find that MCs in the main disk of \flower are globally stable, but their internal substructures have low $\alpha_{\rm vir}$ and $Q_{\rm eff}$ values, indicative of
%mm
    instability to gravitational 
collapse.
%
%Our results suggest that the more massive and bigger MCs compared to the Milky Way manifest from the
%higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
\AF{Abstract is a bit thin. Revise at the end}
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA) can furnish 
%mm scrutinizing 
data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

Such massive gas inflows trigger gravitational instabilities that lead to the formation of molecular 
%mm complexes [first use of this term; did you want "cloud complexes" instead of "complexes" for agreement with abstract?] 
   cloud complexes (MCCs)  \MM{changed MC to MCC throughout}
that are typically more massive ($M_{\rm cl}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%
Some theoretical works argue that the migration of such giant massive clumps are largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

% ------------------
\section{Numerical simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation zoom-in on a target halo of mass $\sim 10^11 \Msun$. The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter (equivalent baryonic) mass resolution is $\simeq 6\times 10^4 \Msun$ ($1.2 \times 10^4 \Msun$). Such region is spatially refined with a quasi-Lagrangian mass threshold-based criterion, i.e. a cell is refined if its total (DM+baryonic) mass exceed the the mass resolution by a factor 8. The final finest refined cell in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$).
%mm
    \MM{Is this really the resolution of dark matter particles?  The baryonic mass (i.e.\ gas) resolution depends on the 
    local density, which would have to be specified here.} \AP{the setting description has been extended}
     Cell sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},
%mm 
     \MM{Nota Bene!} \AP{This note is discussed in details in the following section. In the simulation we do not treat 5--10 cells as MCs, so I would remove the point from the present} although the resolved scale of 5--10 cells is rather larger.
%mm We
    The models include a chemical network 
%mm including ${\rm e}^{-}, \rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ 
   following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that abundances are calculated using an on-the-fly non-equilibrium formation of molecular hydrogen scheme 
%mm following \citet{Pallotini17b} [the order had to be reversed for alphabetization]
    described by \citet{Pallottini17a}.

% radiative feedback --> NT pressure
Star formation is modeled using an H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae (SNe) 
%mm and OB/AGB stars. 
   as well as winds from OB and asymptotic giant branch stars.
Coupling to the gas is implemented via a sub-grid model for blastwaves, which accounts for radiative energy losses inside the cell. The remaining energy is injected into the ISM in kinetic and thermal energy forms. Radiation pressure on dust and gas is also included (see \citealt{Pallottini17a} for details).  
%mm
   \MM{confirm:} Photoionization from local sources is neglected in this simulation \citep[see][for its effect]{pallottini:2019,decataldo:2019}. \AP{modified accordingly}

The simulation zooms in on a galaxy named
%mm 
   after the flower 
\flower whose properties are given in 
%mm \citet{Pallottini17b} 
      \citet{Pallottini17a} 
and are briefly summarized in the following. \flower is a Lyman-break galaxy 
%mm (LBG), [unused acronym]
that at $z\simeq 6$ is hosted by a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of $M_\star\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of $\simeq$\,100\,\Msun\,yr\pmOne. \MM{What is its gas fraction?  I ask because its molecular gas mass is minuscule, particularly for such a high SFR: this is a depletion time of only 0.5 Myr, while modern galaxies usually have depletion times more like 0.5--2~Gyr!} \AP{the gas fraction is very flickering and depends on which radius we are considering, as the galaxy is actively accreating material and merging; depletion time are low, see the ssfr note added considering that $ssfr \propto t_{depletion}^{-1}$} The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq 4 -- 40 \rm Gry ^{-1}$, compatible with sSFR vs $M_{\star}$ relation observed at high-redshift \citep{Jiang2016}, that is higher with respect to normal local galaxies. Its effective stellar radius  is $\sim$0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.

@@

The \SF history\footnote{Note that here the SFR is calculated based on the stellar mass formed in the last 10 Myr within 3.5 kpc from the galaxy center of mass. The SFR plotted in Figure 2 of \citet{Pallottini17b} is a factor of two higher since there the SFR account for the contribution from massive satellite galaxies within the virial radius ($\simeq$15\,kpc).} of \flower is shown in \Fig{SFH}. The SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne as it evolves from an actively accreting phase to a starburst phase after a merger, and then back to a relatively quiescent phase, over the simulated $\simeq 700$ Myr.

@@

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10$-$13 MCCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$. The mass of the MCCs identified ranges between $M_{\rm cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCCs?}

@@

MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$ pc). These values are consistent with those found in starburst galaxies as SMM J2135-0102, located at $z=...$ \AF{Give refs. here and in caption; in addition it would good to give the properties of this galaxy}.
Sizes are somewhat dependent on the choice of $n_{\rm cut}$. As such density threshold is increased, some of the MCCs within the main disk break into multiple sub-MCCs. In this case, we effectively identify a population of denser molecular structures (see \Fig{MCC}). Instead, we find that $\sigma$ is rather insensitive to the actual value of $n_{\rm cut}$.

@@

%
%\begin{comment}
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
%\caption{
%Larson's (linewidth-size) relation of \flower in
%accretion phase (top) and
%starburst phase (bottom) compared to
%those observed in nearby and the \z$\sim$2 star-forming galaxy.
%% Red lines show the relation obtained from \citet{}.
%Observed data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
%\label{fig:larsons_single}}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_alphavir.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_alphavir.png}
%\caption{
%Virial parameter and cloud mass of \flower (star symbols) in the accretion phase (top panel)
%and the starburst phase (bottom panel) compared to the
%Milky Way (other symbols).
%Literature data are compiled from \citealt{Kauffmann17b} and references therein.
%Star symbols are color-coded by $n_{\rm cut}$.
%Star symbols lying close to $\alpha_{\rm vir}\simeq2$ correspond to MCCs in the satellite galaxies.
%\label{fig:alpha16}}
%\end{figure*}
%
%\begin{figure*}[htbp]
%\centering
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss16_PVE.png}
%\includegraphics[trim=0 0 0 0, clip, width=0.65\textwidth]{\figpath/ss27_PVE.png}
%\caption{
%$\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCCs identified in our simulation (star symbols)
%in the accretion phase (top panel) and the starburst phase (bottom panel)
%compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
%The V-shaped dashed lines show the loci along which the given external pressures
%are needed for MCCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
%Similar to \Fig{alpha16}, star symbols are color-coded by $n_{\rm cut}$.
%Star symbols along the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$
%correspond to MCCs in the satellite galaxies.
%\label{fig:alpha27}}
%\end{figure*}
%\end{comment}

@@

The MCCs of \flower has dynamics largely similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, in terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms.
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of these MCCs can also be understood as they have experienced more recent episodes of \SF as \flower is assembling its stellar mass (these MCCs also have higher stellar-to-gas mass ratios of $\sim$60).
%
In fact, by the accretion stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is due in part to the stronger stellar feedback compared to e.g., MCCs in its satellites ($\sigma\simeq$10\,\kms).

@@

Based on the scaling of $M_J$\eq$\sigma^4/(G^2\Sigma)$ for the Jeans mass, a
velocity dispersion of $\sigma\simeq50$\,\kms and a
gas mass surface density of $\Sigma_{\rm gas}\simeq450$\,\Msun\,pc$^{-2}$ yields
$M_J\sim$\,8\E{8}\,\Msun, which is in good agreement with the mass range found in the MCCs identified (see \Fig{dist}).
%
Similarly massive molecular clouds have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum
resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}).
Note, however, that the IGM and merger and accretion histories are not properly modeled in such simulations since they adopt non-cosmological initial conditions. That said, this is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).

@@

% alpha parameters
As shown in \Fig{larsons_single},
the virial parameter of the sub-MCCs is about $\alpha_{\rm vir}\gtrsim10$, which is considerably lower than their ``parent'' MCCs found in the main disk of \flower ($\alpha_{\rm vir}\gtrsim100$).
%
For the MCCs in the satellite galaxies, a lower virial parameter is found compared to the (sub-)MCCs in the main disk of \flower, with $\alpha_{\rm vir}\simeq$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker stellar feedback in the satellites as they have experienced less episodes of \SF compared to \flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1).

@@

We find that the MCC of \flower are highly supersonic, with high velocity dispersions ($\sigma\simeq$\,200\,\kms) comparable to
those observed in $z$\ssim2 starburst galaxies.
The mass scale of the MCCs is of the order of $10^{5.5-8.5}$\,\Msun, depending on the chosen H$_{2}$ cut. 
The $\sim$200\,pc-scale MCCs found with a low density threshold
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCCs at higher density thresholds.
The more massive and bigger MCCs in \flower compared to the Milky Way
likely result from the higher gas mass fraction, surface density, and velocity dispersion,
which set the scale for fragmentation.
This physical scale is
consistent with what has been found in higher resolution idealized simulation of isolated galaxies.
Our simulation here confirms these results at EoR and under
the influence of continuous gas accretion from the surrounding IGM (see e.g., \citealt{Klessen10a, Goldbaum11a}).
